Array Programming with NumPy

### 2020-06-02 methods.tex
Fix references

Bit generators are simple classes that manage the state of an underlying
pseudorandom number generator. NumPy ships with four bit generators. The default
bit generator is a 64-bit implementation of the Permuted Congruential Generator
\cite{pcg64} (\texttt{PCG64}). The three other bit generators are a 64-bit version
of the Philox generator \cite{random123} (\texttt{Philox}), Chris Doty-Humphrey's
Small Fast Chaotic generator \cite{practrand} (\texttt{SFC64}), and the 32-bit
Mersenne Twister \cite{mt19937} (\texttt{MT19937}) which has been used in older
versions of NumPy.\footnote{The
\href{https://github.com/bashtage/randomgen}{randomgen project} supplies a wide
range of alternative bit generators such as a cryptographic counter-based
generators (\texttt{AESCtr}) and generators that expose hardware random number
generators (\texttt{RDRAND}) \cite{randomgen}.} Bit generators provide
functions, exposed both in Python and C, for generating random integer
and floating point numbers. The three new bit generators were chosen for their
combination of statistical soundness and performance. The PCG family of generators
have been widely tested using state-of-the-art statistical tests and found to
perform well (\cite{lemire_blog}). All three of the new generators were tested
using the PractRand test suite (\cite{practrand}) with four TB of random values.
Each was tested using a single generator and using a composite generator assembled
from multiple copies of the same bit generator, each seeded from a shared
\texttt{SeedSequence}.

>>>>

Bit generators are simple classes that manage the state of an underlying
pseudorandom number generator. NumPy ships with four bit generators. The default
bit generator is a 64-bit implementation of the Permuted Congruential Generator
\cite{pcg64} (\texttt{PCG64}). The three other bit generators are a 64-bit version
of the Philox generator \cite{random123} (\texttt{Philox}), Chris Doty-Humphrey's
Small Fast Chaotic generator \cite{practrand} (\texttt{SFC64}), and the 32-bit
Mersenne Twister \cite{mt19937} (\texttt{MT19937}) which has been used in older
versions of NumPy.\footnote{The
\href{https://github.com/bashtage/randomgen}{randomgen project} supplies a wide
range of alternative bit generators such as a cryptographic counter-based
generators (\texttt{AESCtr}) and generators that expose hardware random number
generators (\texttt{RDRAND}) \cite{randomgen}.} Bit generators provide
functions, exposed both in Python and C, for generating random integer
and floating point numbers.
